\section{NAVIGATION}

Note the CMD ALT CNTRL and SHFT on right hand side of keyboard.

General Text.
\begin{easylist}[itemize]
\ListProperties(Style*=$\bullet$ , FinalMark={)}) % FinalMark indicates the end of the list properties and must always be used
& \texttt{SHFT} -- hold to select.
& \texttt{ALT $\leftarrow$ $\rightarrow$} -- jump by word.
& \texttt{CMD $\leftarrow$} -- move cursor to beginning of line.
& \texttt{CMD $\rightarrow$} -- move cursor to end of line.
& \texttt{CMD $\uparrow$} -- move cursor to top of file.
& \texttt{CMD $\downarrow$} -- move cursor to bottom of file.
\end{easylist}

General Apps.
\begin{easylist}[itemize]
\ListProperties(Style*=$\bullet$ , FinalMark={)})
& \texttt{CMD C} -- copy.
& \texttt{CMD X} -- cut.
& \texttt{CMD V} -- paste.
& \texttt{CMD Z} -- undo.
& \texttt{CMD SHFT Z} -- redo.
& \texttt{CMD N} -- new.
& \texttt{CMD O} -- open.
& \texttt{CMD S} -- save.
& \texttt{CMD SHFT S} -- save as.
& \texttt{CMD W} -- close tab.
& \texttt{CMD Q} -- quit.
& \texttt{CMD A} -- select all.
& \texttt{CMD +/-} -- zoom in/out.
& \texttt{CNTRL TAB} -- flick through tabs (use \texttt{SHFT} to reverse).
& \texttt{ALT CMD $\leftarrow$ $\rightarrow$} -- flick through tabs.
& \texttt{CMD <n>} -- select enumerated tab.
\end{easylist}

\vspace{\baselineskip}
\vspace{\baselineskip}

Chrome.
\begin{easylist}[itemize]
\ListProperties(Style*=$\bullet$ , FinalMark={)})
& \texttt{CMD T} -- new tab.
& \texttt{CMD SHFT T} -- re-open closed tab.
& \texttt{CMD L} -- selects location bar.
& \texttt{CMD R} -- reloads page.
\end{easylist}

Finder.
\begin{easylist}[itemize]
\ListProperties(Style*=$\bullet$ , FinalMark={)})
& \texttt{CMD SHFT N} -- create new directory.
\end{easylist}

Mac.
\begin{easylist}[itemize]
\ListProperties(Style*=$\bullet$ , FinalMark={)})
& \texttt{CNTRL $\leftarrow$ $\rightarrow$} -- flick between pages.
& \texttt{CMD space} -- spotlight search.
& \texttt{CMD tab} -- flick between applications (use \texttt{SHFT} to reverse).
& \texttt{F3} -- desktop info.
& \texttt{F4} -- list of apps.
& \texttt{SHFT CMD 3} -- screenshot.
& \texttt{SHFT CMD 4} -- cropped screenshot.
\end{easylist}

Command Line.
\begin{easylist}[itemize]
\ListProperties(Style*=$\bullet$ , FinalMark={)})
& \texttt{CNTRL U} -- delete from beginning to cursor (up).
& \texttt{CNTRL K} -- delete from cursor to end (kill).
& \texttt{CNTRL W} -- delete previous word (word).
& \texttt{CNTRL Y} -- paste previous delete block.
& \texttt{ALT click} -- move cursor to a specific point.
& \texttt{CNTRL A} -- move cursor to beginning of line.
& \texttt{CNTRL E} -- move cursor to end of line.
& \texttt{CMD $\leftarrow$ $\rightarrow$} -- flicks between terminal sessions.
& \texttt{CMD $\uparrow$ $\downarrow$} -- flicks through past commands \bf{clearly}.
\end{easylist}


\vspace{\baselineskip}
\vspace{\baselineskip}
Useful Webpages
\begin{itemize}
  \item \texttt{https://support.apple.com/en-gb/HT201236} - all the mac shortcuts!
\end{itemize}

\newpage