\section{SUBLIME}

Colour schemes can be selected via: Sublime Text $\rightarrow$ Preferences $\rightarrow$ Color Scheme...
\newline
Preferences can be set in: Sublime Text $\rightarrow$ Preferences $\rightarrow$ Settings (\texttt{CMD ,} )
\begin{easylist}[itemize]
\ListProperties(Style*=$\bullet$ , FinalMark={)}) % FinalMark indicates the end of the list properties and must always be used
& \texttt{"auto{\_}find{\_}in{\_}selection": true}
& \texttt{"font{\_}size": 12}
& \texttt{"word{\_}wrap": false}
& \texttt{"translate{\_}tabs{\_}to{\_}spaces": true}
\end{easylist}

Short-Cut basics:
\begin{easylist}[itemize]
\ListProperties(Style*=$\bullet$ , FinalMark={)})
& \texttt{CMD Z} -- undo.
& \texttt{CMD Y} -- redo.
& \texttt{CMD C} -- copy.
& \texttt{CMD X} -- cut.
& \texttt{CMD V} -- paste.
& \texttt{CMD SHIFT V} -- paste with indent.
\end{easylist}

Short-Cut Lines:
\begin{easylist}[itemize]
\ListProperties(Style*=$\bullet$ , FinalMark={)})
& \texttt{CNTRL CMD $\uparrow$ or $\downarrow$} -- swap line up or down.
& \texttt{CMD SHFT D} -- duplicate line (does not use clipboard).
& \texttt{CNTRL SHFT K} -- delete line.
& \texttt{CNTRL K} -- delete line to end.
& \texttt{CMD delete} -- delete line to beginning.
& \texttt{CMD J} -- join lines.
\end{easylist}

Short-Cut Text:
\begin{easylist}[itemize]
\ListProperties(Style*=$\bullet$ , FinalMark={)})
& \texttt{CMD ]} -- indent.
& \texttt{CMD [} -- unindent.
& \texttt{CMD /} -- toggle comments.
& \texttt{CMD ENTER} -- insert line afterwards (don't need to be on end of current line).
& \texttt{CMD SHFT ENTER} -- insert line before.
& \texttt{CNTRL T} -- swaps two characters around (transpose).
& \texttt{CMD K then U} -- convert to upper case.
& \texttt{CMD K then L} -- convert to lower case.
\end{easylist}

Short-Cut Selection. Remember mouse middle button selection:
\begin{easylist}[itemize]
\ListProperties(Style*=$\bullet$ , FinalMark={)})
& \texttt{CMD A} -- select all.
& \texttt{CMD D} -- select word.
& \texttt{CMD L} -- select (full) lines.
& \texttt{CMD SHFT L} -- split into lines.
& \texttt{CNTRL SHFT M} -- select within brackets.
& \texttt{CMD SHFT J} -- select within indentation.
& \texttt{CMD SHFT space} -- select within scope.
\end{easylist}

Find and Replace:
\begin{easylist}[itemize]
\ListProperties(Style*=$\bullet$ , FinalMark={)})
& \texttt{CMD F} -- set up find (press \texttt{escape} to leave). Note the special options available. Select the area you wish to use.
& \texttt{ENTER} -- find next (hold \texttt{SHFT} to reverse this).
& \texttt{ALT ENTER} -- to replace.
\end{easylist}

\newpage